\chapter{Introduction}
\label{cha:Introduction}

\section{Motivation}
\label{sec:Motivation}

Most credentials used by humans are fairly easy to break since they are not
complex enough. When they also have to be shared then any sense of security is
already eliminated since it is written down.

Getting rid of writing down secrets to remember them, and yet still being able
to share them is the motivation behind this paper. While there are already many
applications which help to remember a person's secrets, none of the open source
options allows the user to share these secrets with other people.

Another motivation is to use such software to retrieve secrets required for
application development such as SSH key pairs used by a web application.

\section{Goal of this Paper}
\label{sec:GoalOfThisPaper}

Goal of this paper is to develop an open cryptographic protocol for secure
secret sharing over the internet. This protocol should only use known secure
and well researched algorithms and protocols.

\section{Structure of this Paper}
\label{sec:StructureOfThisPaper}

This paper starts by recapitulating important cryptographic fundamentals,
algorithms and protocols. Subsequently the strategy to achieve secure secret
sharing over the internet will be explained accompanied by discussions of
decisions made. Afterwards strengths, weaknesses and possible attacks of the
defined protocol are examined. This will be followed by a technology basics chapter
and a chapter describing the development. Finishing up, possible future work and
improvements are discussed.
